Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-17 articles/cycle/alps-cycle.tex
ALPCYC: add tentative outline.
This could work for a traditional paper but not for Nature's short format.
I have to check their instructions once again.
Update abstract and title to EGU 2017 version.

\title{Modelling the last glacial cycle in the Alps}

@@

\begin{abstract}
\end{abstract}

>>>>

\title{Modelling last glacial cycle ice dynamics in the Alps}

@@

\begin{abstract}

    The European Alps, cradle of pioneer glacial studies, are one of the
    regions where geological markers of past glaciations are most abundant and
    well-studied. Such conditions make the region ideal for testing numerical
    glacier models based on approximated ice flow physics against field-based
    reconstructions, and vice-versa.

    Here, we use the Parallel Ice Sheet Model (PISM) to model the entire last
    glacial cycle (120--0\,ka) in the Alps, with a horizontal resolution of
    1\,km. Climate forcing is derived using present-day climate data from
    WorldClim and the ERA-Interim reanalysis, and time-dependent temperature
    offsets from multiple paleo-climate proxies, among which only the EPICA ice
    core record yields glacial extent during marine oxygen isotope stages~4
    (69--62\,ka) and~2 (34--18\,ka) in agreement to geological reconstructions.

    Despite the low variability of this Antarctic-based climate forcing, our
    simulation depicts a highly dynamic ice cap, showing that alpine glaciers
    may have advanced many times over the foreland during the last glacial
    cycle. Cumulative basal sliding, a proxy for glacial erosion, is modelled
    to be highest in the deep valleys of the western Alps. Finally, the Last
    Glacial Maximum advance, often considered synchronous, is here modelled as
    a time-transgressive event, with some glacier lobes reaching their maximum
    as early as 27\,ka, and some as late as 21\,ka. Modelled ice thickness is
    about 900\,m higher than observed trimline elevations, yet our simulation
    predicts little erosion at high elevation due to cold ice conditions.

\end{abstract}

\section{Introduction}

\section{Model set-up}
\subsection{Overview}
\subsection{Ice rheology}
\subsection{Basal sliding}
\subsection{Bedrock deformation}
\subsection{Surface mass balance}
\subsection{Climate forcing}
    Fig. -- GRIP and EPICA time series
\subsection{Computing cost}
    Fig. -- Scalability
    Fig. -- Time stamps

\section{Results}
\subsection{Ice cap evolution}
    Fig. -- 21 ka snapshot and time series
\subsection{Ice thickness}
    Fig. -- Trimlines
\subsection{Timing of the LGM}
    Fig. -- Timing of the LGM
\subsection{Total sliding}
    Fig. -- Total sliding
\subsection{Uplift rates}
    Fig. -- Uplift rates

\section{Conclusion}
